Picky with peakpicking: assessing chromatographic peak quality with simple

### 2023-07-31 manuscript/manuscript.Rmd
Fixing reference style for BMC

---
title: 'Picky with peakpicking: assessing chromatographic peak quality with simple
  metrics in metabolomics'
author: "William Kumler, Bryna J. Hazelton, and Anitra E. Ingalls"
output:
  word_document:
    reference_docx: template.docx
bibliography: refs.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval=TRUE)
knitr::opts_knit$set(root.dir = '..')
options(readr.show_col_types = FALSE)
options(tidyverse.quiet = TRUE)
library(tidyverse)
library(RaMS)
```

>>>>

---
title: 'Picky with peakpicking: assessing chromatographic peak quality with simple
  metrics in metabolomics'
author: "William Kumler, Bryna J. Hazelton, and Anitra E. Ingalls"
output:
  word_document:
    reference_docx: template.docx
bibliography: refs.bib
csl: bmc-bioinformatics.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval=FALSE)
knitr::opts_knit$set(root.dir = '..')
options(readr.show_col_types = FALSE)
options(tidyverse.quiet = TRUE)
library(tidyverse)
library(RaMS)
```
